X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-04 hedpc.tex
marcos review of results and discussion

\section*{Discussion}
This work develops Talbot-Lau interferometry to a regime of
high photon energies.
High energies are required for the operation of computed
tomography and security scanners, in order to
penetrate materials with large thicknesses or high atomic number.

Additionally, the dose delivered to the patients could be reduced through
phase sensitivity at high energies: the dose depends mainly on the
absorption and it decreases with the third power of the photon energy~\cite{Momose2005}. On
the other hand, the phase interaction is only inversely proportional to the
energy and is therefore relatively much more relevant than absorption as the
energy increases, possibly leading to a decreased exposure for an equivalent
image quality.

We show the first images on a conventional laboratory source in this energy
range. In fig.~\ref{Fig:img_chip}, several resistors and an integrated
circuit are located on different layers on an electronic chip. The
radiographs were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
calculating the derivative along the horizontal axis. In the attenuation
image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependence of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}\label{Fig:img_chip}
\end{figure}

Edge-on illuminated grating interferometry finally allows phase contrast
imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on
conventional X-ray
sources. With a circular alignment of the gratings, the diffracting and
absorbing structures can be matched to the divergent beam, even for very
compact geometries. Short, high-energy phase-contrast systems enable the
efficient investigation of high-density materials or thick samples,
adding information on electron density and integrated small angle scattering
power to the conventional absorption based signal. This will improve
material discrimination and density sensitivity capabilities in future
X-rays or even neutron~\cite{Grunzweig2008} investigations.

>>>>

Fig.~\ref{Fig:img_chip} shows the first X-ray images acquired with our new setup, based on
edge-on illuminated grating interferometry powered by a conventional X-ray
source operated at \SI{160}{\kilo\voltpeak} and with a design energy of
\SI{100}{\kilo\eV}.  
\begin{figure}[h!]
    \centering
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}\label{Fig:img_chip}
\end{figure}
Several resistors and integrated circuits located on different
layers on an electronic chip can be identified. The radiographs were acquired in scanning
mode, using a step size of \SI{100}{\micro\metre} along the $y$ axis, covering a total imaging
area of $2 \times \SI{2}{\centi\metre^2}$. For a better comparison of the magnified phase and
attenuation images, the latter has been replaced with the differential
attenuation image, which was obtained by calculating the derivative along
the horizontal axis. In the attenuation image, the contrast of the soldering
points of the integrated circuit is reduced underneath the resistors, while
in the phase image, they can clearly be identified. The reduced contrast of
the soldering points in the absorption image is due to beam hardening. The
spectrum impinging on these soldering point is hardened by the resistors in
the upper layer, resulting in lower absorption contrast. Due to the weaker
energy dependence of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast
images are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the lower
contrast reduction of the soldering points under the resistors in the
phase image of the chip. This example shows one of the potential benefits of
phase contrast X-ray imaging at high energies, which may be useful to
identify flaws in multilayered structures such as electronic chips.

\section*{Discussion}

Possible usages of edge-on grating interferometry encompasse applications
ranging from medical imaging to non-destructive testing and homeland
security. All these applications seek for high (greater than
\SI{100}{\kilo\eV}) nominal energies
and compact designs. Particularly for medical application, the operation of
a phase contrast imaging device at high energies is imperative. When imaging
patients, a crucial issue is the dose, which depends mainly on the
absorption of the X-rays and decreases with the third power of the photon
energy~\cite{Momose2005}. On the other hand, the phase interaction is only inversely
proportional to the energy and is therefore relatively much more relevant
than absorption as the energy increases, possibly leading to a decreased
exposure for an equivalent image quality. Clinical operation of such a
device will imply measuring patients who normally breath, move and shake.
Fast acquisitions are therefore required, in order to keep the images sharp
and artefact free. As a consequence, compact, efficient imaging systems need
to be developed to provide imaging capabilities at sufficient speed. Our
circular grating alignment matches the structures of the diffracting and
absorbing elements to the divergent beam, especially for compact geometries.
In conclusion, short, high-energy phase-contrast systems will enable the
efficient investigation of high-density materials or thick samples, adding
information on electron density and integrated small-angle scattering power
to the conventional absorption-based signal. This will improve material
discrimination and density sensitivity in future X-ray or even
neutron~\cite{Grunzweig2008} investigations.
